%-----------EXPERIENCE-----------%
\section{\large \textbf{EXPERIENCE}}
\resumeSubHeadingListStart

    \resumeSubheading
    {Bayer U.S Consumer Health}{Whippany, US}
    {Senior Data Scientist}{Jun 2023 -- Dec 2023}
    \resumeItemListStart
        \resumeItem{New Product Sales Forecasts: Built regression-based models to predict incremental sales opportunity for upcoming Bayer Over-the-counter (OTC) launches, with features based on past similar product introductions in the market. }
        \resumeItem{Generated \textbf{1.7 M\$} in savings with an in-house forecasting engine from 38 product forecasts in partnership with 14 innovation managers. Models tested \textbf{93\%} accurate over a 6-month period.} 
        % \resumeItem{Mentored an intern over Summer’23 who improved team’s flu-season prediction accuracy with innovative features and successfully completed automation projects to improve productivity}
    \resumeItemListEnd
    \resumeSubSubheading
    {Data Scientist}{Jun 2022 -- May 2023}
    \resumeItemListStart
        \resumeItem{\textbf{SKU Demand Forecasting System}: Developed a Gradient Boosted trees \& LSTM based time-series forecasting pipeline for Bayer OTC drug portfolio worth $\sim3B\$ $ (15 brands) to predict 1-year future demand at weekly granularity} 
        \resumeItem{Ensured broad market coverage via features such as weather, promotions, store inventory, competitor sales and illnesses to achieve a Lag 3 accuracy ranging between \textbf{70\%} -- \textbf{85\%} across 200+ SKUs with \textbf{$\pm$5pp} seasonal deviations. Integrated automated accuracy based re-training triggers on Databricks to significantly diminish weekly model maintenance effort}
        % \resumeItem{Integrated automated accuracy based re-training triggers on Databricks with Datarobot as AutoML platform}
        \resumeItem{Consistently recognised for talent receiving Top Performance award in 2023 for leading innovation within the team}
    \resumeItemListEnd
    \vspace{3pt}
    \resumeSubheading
    {Gartner Research \& Advisory}{Gurugram, IN}
    {Senior Business Associate}{Mar 2020 -- Nov 2020}
    \resumeItemListStart
        \resumeItem{Led product development of Python \& SQL data pipelines for an org-wide live client prioritisation tool used by 300+ service associates daily. Reduced monthly reported issues by \textbf{38\%} via Python based automated data quality checks}
        % \resumeItem{Streamlined bug   via Python to reduce monthly reported issues }
        % \resumeItem{Collaborated with multiple scrum teams and product stakeholders to build business roadmap and standardised client outreach metrics across 7 verticals}
    \resumeItemListEnd

    \resumeSubSubheading
    {Quantitative Analyst (NLP) }{Jun 2018 -- Feb 2020}
    \resumeItemListStart
        \resumeItem{Engineered \textbf{Early-Risk Prediction indicators} on client usage patterns to build statistically guided success metrics for service associates. Recorded \textbf{90\%+} recall in identifying churned customers via RandomForest models at multiple contract touchpoints }
        \resumeItem{Innovated a word-vector-based \textbf{Textual Content recommendation algorithm} for suggesting research documents to \textbf{unengaged users} via collaborative filtering. Achieved \textbf{80\%} hits in top-10 results for user profiles across markets and industries}
        %Piloted Flask service with an outreach team that integrated risk predictions with content suggestions to gather associate feedback.
        \resumeItem{Launched a \textbf{Client Feedback Text Classification} service using Multinomial Naive Bayes to publish root causes of service dissatisfaction from client responses with an F1-score of 0.75. Reduced insight analysis time from survey text data by \textbf{50\%} 
        }

        % \resumeItem{Launched a \textbf{Client Feedback Classification} service using Multinomial Naive Bayes to publish root causes of service dissatisfaction from client responses with an F1-score of 0.75 and \textbf{50\%} reduction in reporting time via PowerBI 
        % }
        %Achieved F1-score of 0.75 and implemented a PowerBI \& Python pipeline to reduce monthly reporting time by \textbf{50\%}
    \resumeItemListEnd
    \vspace{7pt}
%\textit{Early-Risk Prediction System}:
    \resumeSubheading
    {Edge Networks}{Bangalore, IN}
    {NLP Research Intern}{May 2017 -- Jul 2017}
    \resumeItemListStart
        \resumeItem{Innovated a Bi-LSTM \& ConvNet strategy in Pytorch on resume embeddings for text classification into suitable job-types. Implemented Attention over embeddings to improve top-10 precision by 30pp. Created on-demand APIs using Flask.}
    \resumeItemListEnd
\resumeSubHeadingListEnd